\subsubsection{3.1.1 Data sources, access, and safeguards}\label{data-sources-access-and-safeguards}

\paragraph{Sources, limits, ethics, and reproducibility}\label{sources-limits-ethics-and-reproducibility}

We constructed the corpus from two authoritative inputs plus one reusable legal filter. First, we accessed litigation materials through CourtListener's RECAP archive via the REST API, querying docket and document endpoints to retrieve filings that may contain corporate speech. For each item, we stored provenance (CourtListener document ID, docket ID, source URL, access timestamp), enforced link-back to the source, and retained only short excerpts necessary to localise the quoted speech, consistent with the service's terms. CourtListener covers U.S. federal and state litigation and prohibits bulk redistribution of filings; we release derived annotations and metadata only. {[}EVID\_COURTLISTENER\_API{]}

Second, to control for company size and improve attribution quality, we constrained speakers to firms in the S\&P 500 by scraping the constituent list and selected company pages. We derived company names, tickers, and officer or board member names for attribution and recorded page titles, URLs, revision IDs, and scrape timestamps for auditability. Because Wikipedia text is licensed under CC BY-SA/GFDL, we use derived metadata only and preserve attribution with the recorded revision identifiers. {[}EVID\_WIKIPEDIA\_SP500{]}

Third, we standardised retrieval around a single speech-law lens by applying a Boolean filter for FTC Section 5 (15 U.S.C. ยง 45), combined with channel and corporate-statement keywords (tweet, press release, earnings call, website, advertisement) and deception terms (deceptive, misleading, false advertising). The query template was applied across the S\&P 500 firm universe to ensure consistent coverage. Extensions for MDL or class-certification targeting are MISSING and will be documented if adopted. {[}EVID\_FTC\_SECTION5\_QUERY{]}

Temporal boundaries for collection were MISSING to MISSING, and the out-of-time anchor date was MISSING. Ethics and licensing: filings are public records; no personal data were processed; licensing constraints are respected (no bulk redistribution; link-back preserved). Reproducibility hooks: CourtListener access and orchestration are implemented in orchestrators/run\_pipeline.py and orchestrators/courtlistener\_orchestrator.py; S\&P 500 metadata scraping is implemented in utils/wiki\_scraper.py; the released dataset is archived at DOI 10.5281/zenodo.16934610. {[}EVID\_COURTLISTENER\_API, EVID\_WIKIPEDIA\_SP500, EVID\_FTC\_SECTION5\_QUERY{]}
